---
title: "Swiss Fertility App"
author: "David Parra"
date: "September 26, 2017"
output: ioslides_presentation 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
suppressPackageStartupMessages(library(plotly))

```

## Swiss Fertility Data

This simple app shows the effect of using different covariates to predict fertility in the Swiss Fertility and Socioeconomic Indicators (1888) Data. 

- The app can be found [here](https://davidcparrar.shinyapps.io/my_first_shinny_app/)
- The Github repo can be found [here](https://github.com/Davidcparrar/DDPShiny)
- The data set is available in R and [here](https://opr.princeton.edu/archive/pefp/switz.aspx)

## Usage

The app is divided in two panels, Inputs and results.

### Inputs

- Select which variables to include in the regression model
- Select which variable (x-axis) will be plotted against Fertility (y-axis) 
- Plot prediction?: select whether the regression line with the corresponding confidence intervals should be shown. 

Once the parameters have been selected the user must click on the submit button to obtain the results.

## Results: Prediction

The app will show the plot with the correspending regression model and the confidence intervals of the prediction

```{r plot, echo = FALSE, warning=FALSE, message=FALSE}
q <- ggplot(data = swiss, aes(y = Fertility))
q <- q + geom_point(aes_string(x = swiss$Agriculture))

prediction <- predict(lm(Fertility ~ Agriculture, data = swiss), interval = "confidence")
predframe <- data.frame( x = swiss$Agriculture, Fertility = prediction[,1], lwr = prediction[,2], upr = prediction[,3])

q <- q + geom_ribbon(data=predframe,aes(ymin=lwr,ymax=upr, x = x),alpha=0.3) + geom_line(data=predframe,aes(y = Fertility, x = x),size = 1.5, colour = "lightblue") + labs(x = "Agriculture")
    
ggplotly(q)
```



## Results: Model 

Finally, under the prediction plot a summary of the parameters of the regression model will be presented to the user

```{r cars, echo = FALSE,comment=""}
table <- signif(summary(lm(Fertility ~ Agriculture, data = swiss))$coefficients, digits = 4)
table
```




